\Title

### 2023-02-09 Grimaldi-etal-BiolCybernetics.tex
methods : A 1

%Let us now define a procedure of animating of natural scene by virtual eye-movements similar to that which was used in neurobiological~\citep{vinje_sparse_2000, baudot_animation_2013} and computational neuroscience~\citep{kremkow_push-pull_2016} studies. 
The goal is to test the model in a motion detection task using a realistic data stream. This type of signal is typically recorded by a Dynamic Vision Sensor (DVS). It is a good representation of the information and is inspired by the information sent by retinal ganglion cells through the optic nerve. Binary events allow the visual system to capture the dynamics of the natural scene and carry out different cognitive tasks quickly and effectively. To train and test our model, we need to define a dataset for which we control the direction and speed of motion.  First of all, let's define a trajectory that is inspired by the biological movements of the eyes. Indeed, these movements allow us to dynamically actuate the centre of vision, or gaze, in the visual field. In animals with a fovea, this is particularly useful as it allows the area with the highest density of photoreceptors in the environment to be moved, for example to a point of interest. A specific mechanism for this is called saccades, which are rapid eye movements that reposition the centre of vision. In humans, saccades are very frequent (on average $2 per second~\citep{dandekar_neural_2012}). They are generated very quickly (about $80~\ms$) and they have a whole range of speeds. On a more microscopic scale, the human gaze moves with a continuous drift similar to a Brownian trajectory~\citep{poletti_head-eye_2015}. In order to maintain the full generality of the task, we will define eye movements using a form of random walk~\citep{engbert_integrated_2011}. 
This approach first defines a finite set of possible 2D movements in polar coordinates. Based on the distribution of biological motions, we simplified it by selecting a set of eye movements as the Cartesian product of $8$ linearly spaced motion directions. Next, we define a gaze trajectory as segments whose duration is drawn from a Poisson distribution with a mean block length of $20~\ms$, similar to a Lévy flight~\citep[p. 289]{mandelbrot_fractal_1982}. Finally, the trajectory is integrated, assuming first that the velocities are sampled uniformly and independently from the set of different motion sets, and second that the motion is uniform during a time segment. The resulting instances yield trajectories that are qualitatively similar to those observed for human eye movements (\seeFig{motion_task}-(left)).

>>>>

The goal is to test the model in a motion detection task using a realistic data stream. This type of signal is typically recorded by a Dynamic Vision Sensor (DVS). It is a good representation of the information and is inspired by the information sent by retinal ganglion cells through the optic nerve. Binary events allow the visual system to capture the dynamics of the natural scene and perform various cognitive tasks quickly and effectively. To train and test our model, we need to define a data set for which we control the direction and speed of motion. Let us now define a procedure for animating a natural scene with virtual eye movements, similar to those used in neurobiological~\citep{vinje_sparse_2000, baudot_animation_2013} and computational neuroscience~\citep{kremkow_push-pull_2016} studies. 
First, let's define a trajectory inspired by the biological movements of the eyes. Indeed, these movements allow us to dynamically actuate the center of vision, or gaze, in the visual field. In animals with a fovea, this is particularly useful because it allows the area with the highest density of photoreceptors in the environment to be moved, for example to a point of interest. A specific mechanism for this is called saccades, which are rapid eye movements that reposition the center of vision. In humans, saccades are very frequent (on average $2 per second~\citep{dandekar_neural_2012}). They are generated very quickly (about $80~\ms$) and have a wide range of speeds. On a more microscopic scale, the human gaze moves with a continuous drift similar to a Brownian trajectory~\citep{poletti_head-eye_2015}. In order to maintain the full generality of the task, we will define eye movements using a form of random walk~\citep{engbert_integrated_2011}.This approach first defines a finite set of possible 2D movements in polar coordinates. Based on the distribution of biological movements, we simplified it by selecting a set of eye movements as the Cartesian product of $8$ linearly spaced movement directions and 3 geometrically spaced speeds. Next, we define a gaze trajectory as segments whose duration is drawn from a Poisson distribution with a mean block length of $20~\ms$, similar to a Lévy flight~\citep[p. 289]{mandelbrot_fractal_1982}. Finally, the trajectory is integrated, assuming first that the velocities are sampled uniformly and independently from the set of different motion sets, and second that the motion is uniform during a time segment. The resulting instances yield trajectories that are qualitatively similar to those observed for human eye movements (\seeFig{motion_task}-(left)).
